---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# opentriviadb

<!-- badges: start -->
<!-- badges: end -->

The goal of opentriviadb is to provide an interface to the [Open Trivia Database](https://opentdb.com/). You can access and download samples of the questions available and make them available from within R.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("condwanaland/opentriviadb")
```
## Example

To download questions, simply call `get_questions()`

```{r example}
library(opentriviadb)
dat <- get_questions(number = 10)
dat
```

You can control the category, difficulty, and type (multiple choice/boolean) of the returned questions

```{r}
dat <- get_questions(10, category = "Sports", difficulty = "easy", type = "multiple")
dat
```

To view all available categories, `opentriviadb` provides a helper function `get_categories`, which provides a dataframe of all available categories.

```{r}
categories <- get_categories()
categories
```


## Roadmap
* Incorporate session tokens to eliminate repeated questions
* Get more than 50 questions by repeatedly hitting the API and saving intermediates
